### 2020-07-18 paper.tex
remove cycle ga

As a final, rather different example in this class, suppose approximate inverses $F_\theta, G_\theta : \mathbb{R}^d \rightarrow \mathbb{R}^d$ are learned neural networks trained via a Cycle GAN objective~\citep{cyclegan} to translate between the latent spaces of two models in a Bayesian model selection problem. A user might implement the following involution:

\begin{center}
\begin{tabular}{c}
{\begin{lstlisting}[basicstyle=\small\ttfamily]
@tracefn h from (tr1, tr2) to (tr3, tr4)
   which_model = @read(tr1, :model, :discrete)
   if which_model == 1
      z = @read(tr1, :z, :continuous)
      z_in_model_2 = F(z)
      @write(tr3, :z, z_in_model_2, :continuous)
      @write(tr3, :model, 2, :discrete)
   else
      z = @read(tr1, :z, :continuous)
      z_in_model_1 = G(z)
      @write(tr3, :z, z_in_model_1, :continuous)
      @write(tr3, :model, 1, :discrete)
   end
end
\end{lstlisting}}
\end{tabular}
\end{center}

However, even though $F_\theta$ and $G_\theta$ are trained with
an objective that encourages $F_\theta(G_\theta(z)) \approx z$, 
this relationship is not exact equality, so the involutive MCMC
framework cannot be directly applied, and the involution check
will fail. This error could be fixed by sampling a proposed value
\textit{near} $F_\theta(z)$ or $G_\theta(z)$, rather than directly applying $F_\theta$
and $G_\theta$ to $z$.

>>>>

%As a final, rather different example in this class, suppose approximate inverses $F_\theta, G_\theta : \mathbb{R}^d \rightarrow \mathbb{R}^d$ are learned neural networks trained via a Cycle GAN objective~\citep{cyclegan} to translate between the latent spaces of two models in a Bayesian model selection problem. A user might implement the following involution:
%
%\begin{center}
%\begin{tabular}{c}
%{\begin{lstlisting}[basicstyle=\small\ttfamily]
%@tracefn h from (tr1, tr2) to (tr3, tr4)
   %which_model = @read(tr1, :model, :discrete)
   %if which_model == 1
      %z = @read(tr1, :z, :continuous)
      %z_in_model_2 = F(z)
      %@write(tr3, :z, z_in_model_2, :continuous)
      %@write(tr3, :model, 2, :discrete)
   %else
      %z = @read(tr1, :z, :continuous)
      %z_in_model_1 = G(z)
      %@write(tr3, :z, z_in_model_1, :continuous)
      %@write(tr3, :model, 1, :discrete)
   %end
%end
%\end{lstlisting}}
%\end{tabular}
%\end{center}

%However, even though $F_\theta$ and $G_\theta$ are trained with
%an objective that encourages $F_\theta(G_\theta(z)) \approx z$, 
%this relationship is not exact equality, so the involutive MCMC
%framework cannot be directly applied, and the involution check
%will fail. This error could be fixed by sampling a proposed value
%\textit{near} $F_\theta(z)$ or $G_\theta(z)$, rather than directly applying $F_\theta$
%and $G_\theta$ to $z$.
